BAI resiliences ten droughts

### 2018-03-17 analysis/bai/trends_resilience_bai.Rmd
add

plotrel <- function(df, v, x, label, XLab, YLab){
  require(ggplot2)
  require(ggrepel)

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=4, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    geom_smooth(method='lm', se=FALSE) +
    xlab(XLab) + ylab(YLab) + geom_smooth(method='lm', se=FALSE, colour="black") +
    geom_text_repel() + 
    annotate("text", x=7, y = 0.5, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE)

@@

sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resilience (Rs) (3year window size)")

sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resistance (Rt) (3year window size)")

sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Recovery (Rc) (3year window size)")

@@

sevRs10 <- plotrel(sdf10, v = "rs", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resilience (Rs) (10year window size)")

sevRt10 <- plotrel(sdf10, v = "rt", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resistance (Rt) (10year window size)")

sevRc10 <- plotrel(sdf10, v = "rc", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Recovery (Rc) (10year window size)")

@@

>>>>

plotrel <- function(df, v, x, label, XLab, YLab, coordX_eq, coordY_eq){
  require(ggplot2)
  require(ggrepel)

@@

  ggplot(df, aes_string(y=paste0(v, "_mean_mean"), x=x, label=label)) + 
    geom_smooth(method='lm', se=FALSE, colour="black") +
    geom_errorbar(mapping = yerrbar) + 
    geom_point(size=4, pch = 21, colour="black", fill="white") + 
    theme_bw() + 
    xlab(XLab) + ylab(YLab) + 
    geom_text_repel() + 
    annotate("text", x=coordX_eq, y = coordY_eq, 
             label=lm_eqn(lm(formulita, df)), parse=TRUE)

@@

sevRs <- plotrel(sdf, v = "rs", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resilience (Rs) (3year window size)", 
        coordX_eq = 7, coordY_eq = 0.5)

sevRt <- plotrel(sdf, v = "rt", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resistance (Rt) (3year window size)",
        coordX_eq = 7, coordY_eq = 0.5)

sevRc <- plotrel(sdf, v = "rc", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Recovery (Rc) (3year window size)",
        coordX_eq = 7, coordY_eq = 0.5)

@@

sevRs10 <- plotrel(sdf10, v = "rs", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resilience (Rs) (10year window size)",
        coordX_eq = 7, coordY_eq = 0.5)

sevRt10 <- plotrel(sdf10, v = "rt", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Resistance (Rt) (10year window size)",
        coordX_eq = 7, coordY_eq = 0.5)

sevRc10 <- plotrel(sdf10, v = "rc", x = 'd_severity', label = 'disturb_year',
        XLab = "Drought Severity", YLab = "Recovery (Rc) (10year window size)",
        coordX_eq = 7, coordY_eq = 0.5)

@@

# relation con drought intensity 
```{r}

intensityRs <- plotrel(sdf, v = "rs", x = 'd_intensity', label = 'disturb_year',
        XLab = "Drought Intensity", YLab = "Resilience (Rs) (3year window size)",
        coordX_eq = -1.5, coordY_eq = 0.5)

intensityRt <- plotrel(sdf, v = "rt", x = 'd_intensity', label = 'disturb_year',
        XLab = "Drought Intensity", YLab = "Resistance (Rt) (3year window size)",
        coordX_eq = -1.5, coordY_eq = 0.5)

intensityRc <- plotrel(sdf, v = "rc", x = 'd_intensity', label = 'disturb_year',
        XLab = "Drought Intensity", YLab = "Recovery (Rc) (3year window size)",
        coordX_eq = -1.5, coordY_eq = 0.5) + ylim(c(0.5,3.5))

pdf(here::here('/out/bai_resiliences_severes', 'rs_vs_drought_3years_intensity.pdf'), width=18, height = 7)
intensityRt + intensityRc + intensityRs 
dev.off()
```
